### 2022-07-03 manuscript/manuscript.Rmd
figure 1 update

@@

A total of `r n_sample` subjects with BCH (females, `r n_sex["F", stat]`; males, `r n_sex["M", stat]`) were assessed.

@@

@@

@@

```{r}
y_vars <- c("CM" = "comunicacion_total"
            , "FM" = "motora_fina_total"
            , "GM" = "motora_gruesa_total"
            , "CG" = "resolucion_problemas_total"
            , "personal-individual" = "socio_individual_total")

@@

[**Figure 1**]{#fig1}. Relationship between corrected age (in months) and developmental domains. Left panel: regression lines and shaded area represent predicted values estimated from GAM models and their CI~95%~, points and error bars represent the mean and standard error at 5-month age intervals. Right panel: effect derivatives representing how the effect of corrected age (in months) in developmental domains changes across corrected age. Significant areas consider CI~95%~ that did not cross zero.

>>>>

## Study design

We conducted an observational, cross-sectional study, under a quantitative approach.

[¿Los datos vienen de algún grupo de estudio o de cohorte en particular?]{custom-style="ErrorTok"}

[¿Qué resguardos éticos se consideran? Comité de ética y otros permisos que sean pertinentes]{custom-style="ErrorTok"}

@@

[¿Cómo fueron reclutados los sujetos? Criterios de elegibilidad, tipo de muestreo, etc.]{custom-style="ErrorTok"}

[¿Cómo, cuando y quien hizo el diagnóstico de hipotonía congénita?]{custom-style="ErrorTok"}

@@

[¿Como, cuando y quién recolectó los datos demográficos?]{custom-style="ErrorTok"}

@@

[¿Cómo se evaluó el ASQ-3? ¿Con qué protocolo? ¿Que consideraciones se tuvieron en la evaluación? ¿Algo más que podría ser relevante para agregar respecto a la evaluación o corrección del cuestionario?]{custom-style="ErrorTok"}

@@

```{r}
y_vars <- c("CM" = "comunicacion_total"
            , "FM" = "motora_fina_total"
            , "GM" = "motora_gruesa_total"
            , "CG" = "resolucion_problemas_total"
            , "PS" = "socio_individual_total")

@@

[**Figure 1**]{#fig1}. Relationship between corrected age (in months) and developmental domains. Left panel: regression lines represent predicted values estimated from GAM models (red lines) and 100 bootstrap replicates (gray lines), points and error bars represent the mean and standard error at 5-month age intervals. Right panel: effect derivatives and their CI~95%~, representing how the effect of corrected age (in months) in developmental domains changes across corrected age. Significant areas consider CI~95%~ that do not cross zero.
